The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multiphase Forest Inventories

### 2017-08-18 JStatSoft_forestinventory_master-concordance.tex

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 121 1 1 4 1 1 1 4 3 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 128:%
1 95 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 224:%
136 34 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 259:%
1 84 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 344:%
172 15 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 360:%
1 124 1 1 2 4 0 1 2 14 1 1 5 7 0 1 2 2 1 1 2 24 0 1 2 4 1 1 2 4 0 1 2 2 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 156 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 5 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 888:%
189}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 889:%
1 92 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 982:%
191 10 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 993:%
1 13 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1007:%
203 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1016:%
1 20 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1037:%
213 9 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1047:%
1 20 1 1 4 6 0 1 2 2 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 24 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 79 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1289:%
224 20 1}

>>>>

\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:%
1 121 1 1 4 1 1 1 4 3 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Introduction.Rnw:ofs 128:%
1 95 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 224:%
136 34 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Main structure and modules of the Package.Rnw:ofs 259:%
1 84 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 344:%
172 15 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Twophase_Estimators and their Application.Rnw:ofs 360:%
1 124 1 1 2 4 0 1 2 14 1 1 5 7 0 1 2 2 1 1 2 24 0 1 2 4 1 1 2 4 0 1 2 2 1 1 2 1 0 1 5 6 0 1 2 3 1 1 2 8 0 1 2 156 1 1 7 6 0 1 1 26 0 1 2 3 1 1 2 13 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 5 1 1 6 5 0 1 1 8 0 1 2 7 1 1 2 4 0 1 2 1 1 1 6 5 0 1 1 3 0 1 2 1 1 1 2 11 0 1 2 3 1 1 6 5 0 1 1 8 0 1 2 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 888:%
189}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Threephase_Estimators and their Application.Rnw:ofs 889:%
1 92 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 982:%
191 10 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Calculation of Confidence Intervals.Rnw:ofs 993:%
1 13 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1007:%
203 8 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Special Cases and Scenarios.Rnw:ofs 1016:%
1 20 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1037:%
213 15 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Analysis and Visualization.Rnw:ofs 1053:%
1 20 1 1 4 6 0 1 2 2 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 2 1 1 6 8 0 1 2 2 1 1 7 9 0 1 2 4 1 1 5 7 0 1 2 6 1 1 2 4 0 1 2 2 1 1 2 26 0 1 2 16 1 1 4 1 1 1 2 11 0 1 2 18 1 1 5 7 0 1 2 4 1 1 3 5 0 1 2 10 1 1 2 4 0 1 2 36 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1308:%
230 3 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:./rnw/Acknowledgements.Rnw:ofs 1312:%
1 4 1}
\Sconcordance{concordance:JStatSoft_forestinventory_master.tex:JStatSoft_forestinventory_master.rnw:ofs 1317:%
235 11 1}
